---
title: "Getting Started"
author: "Matthew Strasiotto"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This document aims to provide an overview of the basic usage of the Path object.
Before we start, we load the package.

```{r}
library(pathlibr)
library(here)
library(glue)
```

# Motivation

The Path class aims to make navigating directories a little more convenient, 
it provides convenient interfaces for common operations such as navigating up
(To the parent directory), listing child directories, and joining paths.

# Getting Started

## Making a Path

First lets initialize a new path object.

```{r}
root <- Path$new(system.file("", package = "pathlibr", mustWork = TRUE))
```

And lets view the new path

```{r}
root$show
```
So far so good, we were able to initialize a Path object at our package install
root.

Now how do we use it?

## Navigating with your path

Lets go down a level, and examine our example vignette data.


Here, we use the `dir` binding, followed by `.`

Think of `.` as in, how file-systems represent
the current directory. 

This is actually just a shortcut for `dir` or `ls`. 

```{r}
eg <- root$dir$example
print(glue("using dir: {eg$show}"))

eg <- root$.$example

print(glue("using '.': {eg$show}"))
```

It's important to note that `path$.` is actually returning a named list
of files in the directory, and that though these files might look like 
strings when printed, they're actually new `Path` objects.

Because of this, we're able to chain subsequent `$.` commands.

Let's see that in action.

```{r}
file <- eg$.$path$.$to$.$file1.txt

file
```

Great, so how do we navigate to `file1.txt`'s sibling, `file2.txt`?

We could use the `path$parent` binding to return the `Path` object 
corresponding to the directory `example/path/to/`, 

as you may have guessed, we can use a shortcut alias, `path$..` to navigate up.

```{r}
file$parent

file$..
```

Now that we're able to move upwards, we can access the sibling

```{r}
file2 <- file$..$.$file2.txt

file2$show
```

I wonder what's inside these files? To find out, we should read them.

It's important to notes that we should use this `$show` binding to return
the path as a string when giving it to IO functions. 

Inconvenient, I know (I'm going to work on that)

```{r}
directory <- file$..

for (f in c("file1.txt", "file2.txt")){
  print(glue("{f}:\n"))
  
  directory$.[[f]]$show %>% readLines() %>% cat()
  
  print(glue("\n"))
}

```

